\documentclass{article}

%%% Removes indents at the start of paragraphs
\usepackage[parfill]{parskip}

%%% Landscape
\usepackage[
    landscape,
    margin=1cm,
    tmargin=2cm
]{geometry}

%%% Multiple columns
\usepackage{multicol}
\setlength{\columnsep}{1cm}

\input{../misc_sheets/template/Craftables.tex}

%%% Used for header
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{Drav Daava}
\chead{Craftables}
\rhead{Cheat Sheet}

%%% Reduce amount of space around sections
\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{3ex}{0ex}
\titlespacing{\subsection}{0pt}{0ex}{0ex}
\titlespacing{\subsubsection}{0pt}{0ex}{0ex}

\begin{document}
\begin{multicols*}{3}
\category{Bombs}{Spark-Craft}
Drawback (Conspicuous).
\\\\
% Grenade
\bandcreation{Grenade}{3}{2}{2}
A small explosive charge with a short fuse that detonates into metal shrapnel.
\\\\
% Large Bomb
\bandcreation{Large Bomb}{5}{1}{0}
A large explosive charge with a long fuse.
\HasAmount
\\\\
% Smoke Bomb
\bandcreation{Smoke Bomb}{2}{2}{2}
Creates a cloud of acrid smoke that's difficult to breathe and stings the eyes.


\category{Drugs}{Alchemical}
Drawback (Volatile): ``Woozy'' lvl 1 harm.
\\\\
% Black Lotus
\bandcreation{Black Lotus}{1}{1}{0}
\textit{A tar-like resin made from the leaves of the plant.
Induces coma-like stupor and visions.}
\HasAmount
\\\\
% Bloodneedle
\bandcreation{Bloodneedle}{1}{3}{0}
\textit{Induces fever, euphoric mania, rampant energy.}
\HasAmount
\\\\
% Dream Smoke
\bandcreation{Dream Smoke}{1}{3}{0}
\textit{A milder formulation of black lotus.
Induces a pleasant intoxication.}
\HasAmount
\\\\
% Quicksilver
\bandcreation{Quicksilver}{4}{1}{2}
\textit{A toxic metallic fluid.
The user's mind opens further to the ghost field.}
Take +1d to \skillname{Attune} roll upon use, \suffertempharm{2}{Zoned-out}.
\\\\
% Spark
\bandcreation{Spark}{1}{3}{2}
\textit{A measure of raw electroplasm blended with seawater.
The user feels empowered and emits mild electrical energy.}
\\\\
% Trance Powder
\bandcreation{Trance Powder}{1}{3}{2}
\textit{A glittering blue powder.
Induces a pleasant hypnotic trance when inhaled.}


\category{Oils}{Alchemical}
% Alcahest
\bandcreation{Alcahest}{3}{1}{2}
\textit{A fluid that stops the effect of any other alchemical.}
\\\\
% Binding Oil
\bandcreation{Binding Oil}{3}{1}{2}
\textit{Permanently fuses two surfaces until dissolved by alcahest or electroplasm.}
\\\\
% Fire Oil
\bandcreation{Fire Oil}{3}{3}{2}
\textit{Erupts in searing flame upon contact with air.}


\category{Poisons}{Alchemical}
Drawback (Volatile): ``Sickened'' lvl 1 harm.
\\\\
% Drown Powder
\bandcreation{Drown Powder}{3}{2}{2}
\textit{A fine dust that incapacitates by giving the sensation of drowning.}
\\\\
% Eyeblind
\bandcreation{Eyeblind}{3}{3}{2}
\textit{A powder that causes blindness for a moment.}
\\\\
% Skullfire
\bandcreation{Skullfire}{3}{1}{2}
\textit{Toxic fumes from overly heated leviathan blood.
Causes incapacitating migraines.}
\\\\
% Standstill
\bandcreation{Standstill}{4}{1}{2}
\textit{A powder that causes temporary paralysis.}


\category{Potions}{Arcane}
Drawback: 4-clock, ``Accosted by Spirit Wardens'', 1 tick per use.
\\\\
% Silence Potion
\bandcreation{Silence Potion}{3}{1}{0}
\textit{Creates an area of utter silence around the shattered vial.}
\HasAmount
\\\\
% Shadow Essence
\bandcreation{Shadow Essence}{3}{1}{0}
\textit{A distillation of the void.
Creates a cloud of unnatural pitch darkness.}
\HasAmount
\\\\
% Viper Potion
\bandcreation{Viper Potion}{4}{1}{0}
\textit{The user's saliva and blood become highly toxic for a few minutes.}
\HasAmount


\section*{\uppercase{Special}}
% Drift oil
\bandspecialcreation{Drift Oil}{2}{1}{Arcane}{2}
\textit{Creates neutral buoyancy when poured on an object, causing it to float in the air for an hour.}
\\\\
% Healing Salve
\bandspecialcreation{Helande Salva}{3}{1}{Alkemisk}{1}
\textit{Påskyndar återhämtning från alla sorters skador.}
+4 ticks till healing-klockan.
\textbf{Rare}.
\HasAmountRare
\\\\
% Glidmedål
\bandspecialcreation{Glidmedål}{1}{3}{Alkemisk}{2}
\textit{Gör en yta väldigt hal.}
Har ej lärt mig än!


\section*{Drawbacks}
\begin{itemize}
    \labeleditem{Complex}
    You'll have to create it in multiple stages; the GM will tell you how many.
    One downtime activity and crafting roll is needed per stage.
    %
    \labeleditem{Conspicuous}
    Take \textbf{+1 \uppercase{heat}} if it's used any number of times on an operation.
    %
    \labeleditem{Consumable}
    This creation has a limited number of uses (all alchemicals must have this drawback, usually one use).
    %
    \labeleditem{Rare}
    This creation requires a rare item or material when it is crafted.
    %
    \labeleditem{Unreliable}
    When you use this item, make a fortune roll (using its \textbf{quality}) to see how well it performs.
    %
    \labeleditem{Volatile}
    The item produces a dangerous or troublesome side-effect for the user.
    A side-effect is a consequence, and may be \textbf{resisted}.
\end{itemize}

\textit{
    Note: Alchemicals, bombs, and dangerous gadgets are highly restricted in Doskvol.
    When you use the \textbf{acquire asset} downtime activity to get one of these (rather than crafting it yourself), you take \textbf{+2 \uppercase{heat}}
}


\section*{Bandolier notations}
\begin{itemize}
    \labeleditem{G}
    Cannot fit into the bandolier, will take up a gadget slot.
    %
    \labeleditem{b}
    Can fit into the bandolier but needs to be crafted before it can be placed there.
    %
    \labeleditem{B}
    Refills automatically into the bandolier, no need to craft.
\end{itemize}

\end{multicols*}
\end{document}