\documentclass{article}

%%% Landscape
\usepackage[landscape]{geometry}

%%% Multiple columns
\usepackage{multicol}
\setlength{\columnsep}{1cm}

\input{../misc_sheets/template/Craftables.tex}

%%% Used for header
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{Leech}
\chead{Bandolier}
\rhead{Cheat Sheet}

%%% Reduce amount of space around sections
\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{3ex}{0ex}
\titlespacing{\subsection}{0pt}{0ex}{0ex}
\titlespacing{\subsubsection}{0pt}{0ex}{0ex}

\begin{document}
\begin{multicols*}{3}
\category{Bombs}{Spark-Craft}
Drawback (Conspicuous).
\\\\
% Grenade
\creation{Grenade}{3}{2}
A small explosive charge with a short fuse that detonates into metal shrapnel.
\\\\
% Smoke Bomb
\creation{Smoke Bomb}{2}{2}
Creates a cloud of acrid smoke that's difficult to breathe and stings the eyes.


\category{Drugs}{Alchemical}
Drawback (Volatile): ``Woozy'' lvl 1 harm.
\\\\
% Quicksilver
\creation{Quicksilver}{4}{1}
\textit{A toxic metallic fluid.
The user's mind opens further to the ghost field.}
Take +1d to \skillname{Attune} roll upon use, \suffertempharm{2}{Zoned-out}.
\\\\
% Spark
\creation{Spark}{1}{3}
\textit{A measure of raw electroplasm blended with seawater.
The user feels empowered and emits mild electrical energy.}
\\\\
% Trance Powder
\creation{Trance Powder}{1}{3}
\textit{A glittering blue powder.
Induces a pleasant hypnotic trance when inhaled.}


\category{Oils}{Alchemical}
% Alcahest
\creation{Alcahest}{3}{1}
\textit{A fluid that stops the effect of any other alchemical.}
\\\\
% Binding Oil
\creation{Binding Oil}{3}{1}
\textit{Permanently fuses two surfaces until dissolved by alcahest or electroplasm.}
\\\\
% Fire Oil
\creation{Fire Oil}{3}{3}
\textit{Erupts in searing flame upon contact with air.}


\category{Poisons}{Alchemical}
Drawback (Volatile): ``Sickened'' lvl 1 harm.
\\\\
% Drown Powder
\creation{Drown Powder}{3}{2}
\textit{A fine dust that incapacitates by giving the sensation of drowning.}
\\\\
% Eyeblind
\creation{Eyeblind}{3}{3}
\textit{A powder that causes blindness for a moment.}
\\\\
% Skullfire
\creation{Skullfire}{3}{1}
\textit{Toxic fumes from overly heated leviathan blood.
Causes incapacitating migraines.}
\\\\
% Standstill
\creation{Standstill}{4}{1}
\textit{A powder that causes temporary paralysis.}


\category{Potions}{Arcane}
Drawback: 4-clock, ``Accosted by Spirit Wardens'', 1 tick per use.

\section*{Special}
% Drift Oil
\specialcreation{Drift Oil}{3}{1}{Arcane}
\textit{Creates neutral buoyancy when poured on an object, causing it to float in the air for an hour.}


\section*{Drawbacks}
\begin{itemize}
    \labeleditem{Conspicuous}
    Take \textbf{+1 \uppercase{heat}} if it's used any number of times on an operation.
    \labeleditem{Volatile}
    The item produces a dangerous or troublesome side-effect for the user.
    A side-effect is a consequence, and may be \textbf{resisted}.
\end{itemize}

\end{multicols*}
\end{document}